From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-07 Pi+/paper/finite.tex
Start revising introduction

Constructors $\longcancel$ and $\longswap$ correspond directly to the appropriate constructors of $\cox$ and can be
visualised in the same way as before. The remaining constructor uses the helper function to exchange the order of a long
sequence of transpositions and a single transposition afterwards. For example, for $n = 0$ and $k = 3$, it allows for
the reduction $[4, 3, 2, 1, 0, 4] \longcox [3, 4, 3, 2, 1, 0]$ (see~\Cref{fig:longcox}).

>>>>

Constructors $\longcancel$ and $\longswap$ correspond directly to the appropriate constructors of $\cox$ and can be
visualised in the same way as before. The remaining constructor uses the helper function to exchange the order of a long
sequence of transpositions and a single transposition afterwards. For example, for $n = 0$ and $k = 3$, it allows for
the reduction $[4, 3, 2, 1, 0, 4] \longcox [3, 4, 3, 2, 1, 0]$ (see~\Cref{fig:longcox} -- note the distinction between
wires, where numbers represent the values, and transpositions, where numbers represent which wires are crossing).
